This Ph.D. thesis wouldn't have been possible without the involvement and support from so many people in my life. I decided to become a physicist a long time ago, not knowing what it really meant to be one. Since then, I have been impacted with love and guidance at all stages, and I am so thankful for all of it.

First and foremost, I would like to thank my advisor \textbf{Gabriella Sciolla}. I still remember our call before I joined Brandeis when you told me about your vision for how my Ph.D. would look like, and I have achieved everything you promised, and more. I am incredibly grateful for every opportunity, advice, and feedback I have received from you in the last five years. Thank you for not giving up on me when my vision would not align with yours, and always making sure I did what is best for me (even if it took a bit (a lot) of convincing). What I have learnt from you, especially in the last year, made me a more confident and well-rounded scientist, and that is something I will forever keep with me. There is only one person who wanted me to excel in this journey even more than I did, and that is you.

I would like to thank the other members of my thesis defense committee, \textbf{Aram Apyan} and \textbf{Max Goblirsch} for the thorough review of my thesis and the challenging round of questioning during my defense. Aram, thank you for being my second advisor acting as a sounding board when I needed it. I will cherish our Luigia dinners and I look forward to more (I will order whatever you will)! Max, you have read my thesis more times than I have, making sure I add every missing piece that would make it more complete. I have learnt so much from you in the last two years, ranging from running Athena to understanding the intricacies of limit setting, and acknowledging all of it will take a lot more than a few paragraphs. You will always be an inspiration to me, and I can only hope to become as good a physicist and human being as you one day. I promise to learn how to get better at making money the quick way, and to never check my memory leaks.

I am grateful for my amazing postdocs, \textbf{Guglielmo Frattari} and \textbf{Dominique Trischuk}. Tacchino, you have taught me to approach science with practicality rather than idealism, that sometimes good is better than perfect, and that the one who gets work done is the MVP. I will dearly miss the banter that we shared and I hope that you never stop sending me funny reels. Dominique, you have taught me to take ownership of and pride in my work, to lead from the back when the opportunity presents, and that I don't need to be miserable to be successful. I will keep making you buy me coffees and cookies no matter where we are.

In my time at BNL, I had the pleasure of working with some incredible scientists on hardware and analysis. I want to thank \textbf{Dr. Dave Lynn} for being an amazing mentor for my ITk work. You taught me how to solve problems at the most fundamental level and approach tasks with a scientific temperament. I also want to thank \textbf{Stefania Stucci} for her gentle yet impactful teaching, and also for sharing funny jokes and delicious food with me. Thanks to \textbf{Dr. Alessandro Tricoli} for welcoming me into the $H\to WW^*$ team and giving me the opportunity to work on critical tasks related to such a complex measurement. Thanks to \textbf{Laura Bergsten} and \textbf{Gaetano Barone} for supervising me in the analysis and setting me up for independence. Gaetano, I appreciate your honest advice at every stage of my Ph.D., and I wish that someday I have at least half as many passports as you have. Thanks to \textbf{Jiayi Chen}, \textbf{Guy Rosin}, and \textbf{Chara Kitsaki} for being such great peers and for sharing tasks when I was occupied with coursework or teaching. 

This work wouldn't have been possible without my colleagues in the displaced HNL team, and I would like to thank them for their contributions to all the aspects of the analysis. Thanks to the members of the SUSY displaced leptons team for pushing the LRT lepton development in parallel, accelerating both of our timelines together. I have had the pleasure of interacting with some amazing physicists during my Ph.D. outside the context of my analysis. Thanks to \textbf{Johannes Junggeburth} for teaching me everything about muons and muon reconstruction. Thanks to \textbf{Haider Abidi} for always giving me sound career advice. Thanks to \textbf{Robin Hayes} for always being a skype message away from all kinds of help. Thanks to \textbf{Audrey Kvam} for teaching me about muon triggers, and always willing to share gossip over coffee.

The students of the Brandeis hep-ex group have been my strongest support throughout this journey. Thanks to \textbf{Laura Bergsten} for your guidance in $H\to WW^*$. Thanks to \textbf{Francesca Capocasa} for teaching me everything about LabVIEW, for the amazing times in Ridge, for teaching me how to make pizza, and for the exciting trips to Hicksville. Thanks to \textbf{Jiayi Chen} for always being there to listen to my complaints, for all the car rides whenever I needed them, and for being a great friend always. Thanks to \textbf{Prajita Bhattarai} for being the best roommate one could ask, for teaching me to go easier on myself, and for nudging me to be less grumpy and more grateful. Thanks to \textbf{Zach Schillaci} for helping ease my move to Geneva. Thanks to \textbf{Todd Zenger} for your joyful companionship at BNL and at CERN. Thanks to \textbf{Emily Duden} for listening to my late night rants in Waltham, for being someone I can always joke with, and for happily lending your couch. Thanks to \textbf{Siddharth Singh} for being such an amazing friend whom I can always trust and rely on. 

I also want to thank the Brandeis GSAS administration for making the process of moving from India to BNL to Brandeis to CERN very convenient, especially \textbf{Joan Thorne} and \textbf{Anne Lazerson}. Special thanks to the \textbf{UChicago Tier-3 cluster} for giving my analysis jobs a higher priority in the days leading to my thesis submission, without which I wouldn't have managed to meet the deadlines.

I have made many friends along the way, and my Ph.D. would not have been as pleasant without any of them. Thanks to my wingmates from IITB, \textbf{Deepesh Singh}, \textbf{Aditya Singh}, \textbf{Abhijeet Melkani}, \textbf{Sanyam Chouksey}, and \textbf{Amey Sharma} for being my support system during my time there.
Thanks to \textbf{Punit Sharma} for truly being there for me from the beginning to the end. We started this together, and we will go a long way together. Thanks to \textbf{Arkya Chatterjee} for always being ready to explore Boston or share your room with me. Thanks to \textbf{Andrew Smith} for being my first friend in Geneva and for introducing me to so many amazing people whom I call friends today. Thanks to the \textit{l u n} chat for your constant presence and support, and for never making me feel left out no matter how occupied I was. Thanks to \textbf{Dev}, \textbf{Elena}, \textbf{Tom}, \textbf{Eleanor}, \textbf{Antti}, \textbf{Kevin}, \textbf{Laura}, \textbf{Lauren}, \textbf{Bruno}, \textbf{Ki Ryeong}, \textbf{Sylvia}, and \textbf{Michelle}. I could never have enough of the CERN lunches, BDP sauna Mondays, trivia Tuesdays, ski trips, movie nights, or any moment that I can share with you all.

To my family, \textbf{\textit{amma}}, \textbf{\textit{nanna}}, \textbf{Vinit}, and \textbf{Kalyani} for all the love. Special shout-out to my \textit{pinnis} who have always cheered for me.

Finally, to \textbf{Shivani}, for the unconditional support and understanding throughout this whole thing. I couldn't have asked for more.