\documentclass{brandeis-dissertation3.14}

\usepackage{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage[sorting=none]{biblatex}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{color}
\usepackage{xspace}
\usepackage{tabularx}\usepackage{calc}\usepackage{array}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{titlesec}
\usepackage[compat=1.1.0]{tikz-feynman}
\tikzfeynmanset{warn luatex=false}
\usepackage{Dissertation_Addepalli-defs}
\usepackage{placeins}
\usepackage[hypertexnames=false]{hyperref}
\usepackage{cleveref}

%\renewcommand\thechapter{\Roman{chapter}}
%\renewcommand\thesection{\arabic{section}}

\addbibresource{Dissertation_Addepalli.bib}

\title{A Search for Long-Lived Heavy Neutral Leptons in Events with Displaced Vertices using the ATLAS Experiment}
\author{Sagar Vidya Addepalli}
\graduationmonth{May}
\graduationyear{2024}
\program{Department of Physics}
\advisor{Gabriella Sciolla}
\signoff{Charles Golden}{Dean}
\committee{Prof. Gabriella Sciolla, Department of Physics,\\
Prof. Aram Apyan, Department of Physics,\\
Dr. Maximilian Emanuel Goblirsch-Kolb, European Organization for Nuclear Research}

\begin{document}

\maketitlepage
\makeapproval
%\makecopyright
%\frontmatter
\setlength{\cftchapnumwidth}{3em}
\setlength{\cfttabnumwidth}{3em}
\setlength{\cftfignumwidth}{3em}

\begin{dissertation-acknowledgements}

\end{dissertation-acknowledgements}
%\addcontentsline{toc}{section}{Acknowledgements}

\begin{dissertation-abstract}
The existence of right-handed neutrinos with Majorana masses below the electroweak scale and in the sensitivity range of the LHC could give rise to the smallness of neutrino masses and matter-antimatter asymmetry in the universe. This analysis searches for long-lived right-handed neutrinos, called heavy neutral leptons (HNLs), produced through a $W$ boson decaying into a muon (electron) and a muon (electron) (anti-)neutrino that will mix with an HNL. The ATLAS reconstruction chain went through significant improvements in preparation for data taking in 2022. The improved techniques for reconstructing the displaced signature of the long-lived HNL are applied to 140.1 fb$^{-1}$ of data used in this analysis collected at $\sqrt{s}=13$ TeV in 2015--2018. The search results are interpreted in scenarios where the HNL mixes with one more Standard Model neutrino.
\end{dissertation-abstract}
%\addcontentsline{toc}{section}{Abstract}

\doublespacing
\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

\addtocontents{toc}{\protect\setlength{\cftchapnumwidth}{5em}}
\addtocontents{toc}{\protect\setlength{\cftsecnumwidth}{3em}}
\addtocontents{toc}{\protect\setlength{\cftsubsecnumwidth}{3em}}

\tableofcontents
\clearpage

\listoftables
%\addcontentsline{toc}{section}{List of Tables}
\pagebreak
\listoffigures
%\addcontentsline{toc}{section}{List of Figures}
\pagebreak
\setcounter{secnumdepth}{0}
\chapter*{List of Abbreviations}
%\addcontentsline{toc}{section}{List of Abbreviations}
\input{list-of-abbs}
\setcounter{secnumdepth}{2}

\startbody

%\renewcommand\thefigure{\arabic{figure}}
%\setcounter{figure}{0}
%\renewcommand\thetable{\arabic{table}}
%\setcounter{table}{0}

\chapter*{Introduction}
\label{chap:intro}

\addcontentsline{toc}{chapter}{Introduction}
\input{chapters/introduction}

\chapter{Theory}
\label{chap:theory}
\input{chapters/theory}

\chapter{Experimental Apparatus}
\label{chap:experiment}
\input{chapters/experiment}

\chapter{Analysis Overview}
\label{chap:ana_overview}
\input{chapters/analysis_overview}

\chapter{Analysis Strategy}
\label{chap:ana_strategy}
\input{chapters/analysis_strategy}

\chapter{Results}
\label{chap:results}
\input{chapters/results}

\chapter{Conclusion}
\label{chap:conclusion}
\input{chapters/conclusion}

\addcontentsline{toc}{chapter}{References}
\renewcommand{\bibname}{References}
\singlespacing
%\setlength{\bibitemsep}{0pt plus 1ex}
\printbibliography

\doublespacing
\renewcommand{\thechapter}{\Alph{chapter}}
\renewcommand{\chaptertitlename}{Appendix}
\setcounter{chapter}{0}
%\part*{Appendices}
\addcontentsline{toc}{part}{Appendices}

\chapter{Personal Contributions}
\label{chap:pers_contri}
\input{chapters/personal_contributions}

\chapter{HNL Mass Reconstruction}
\label{chap:HNL_mass}
\input{chapters/HNL_mass}

\chapter{Asymptotic Approximation versus Toys}
\label{chap:asymp_vs_toys}
\input{chapters/toys_vs_asymptotic}

\end{document}