\vspace{1in}
{
``I can thank the fact that I was born at just the right time. A few years older or younger, I would have missed the opportunity... One might call the period from 1925 onward for a few years the Golden Age of Physics when our basic ideas were developing very rapidly and there was plenty of work for everyone to do."

\hfill -Paul Dirac, J. Robert Oppenheimer Memorial Prize Speech, 1969}
\vspace{1in}

The Standard Model of Particle Physics, in its current form, is the most (or even the only) widely accepted complete theory of the particle nature of the universe. It provides a mathematical description of the three out of four fundamental forces of nature: Weak force, Strong force, and the Electromagnetic force. After its full formulation circa 1975, the model has proved to be extremely successful in predicting natural phenomena at the smallest of scales and highest of energies. Nevertheless, a few but critical open problems challenge the foundations and completeness of the Standard Model, and beg for theoretical extensions that can provide solutions to these problems. A large number of extensions to the Standard Model predicting long-lived particles~\cite{Curtin_2019, Alimena_2020} offer such solutions. At the Large Hadron Collider, long-lived particles can decay far from the proton--proton interaction vertex and produce signatures that are distinct from promptly decaying particles, which constitute most of the searches at the LHC. One such signature is a displaced vertex coming from a long-lived particle decaying within the detector volume of ATLAS producing reconstructible particles. In 2022, the ATLAS experiment's reconstruction algorithms went through a significant overhaul~\cite{atlascollaboration2023software, IDTR-2021-03} adding unprecedented sensitivity to long-lived particles searches, especially those probing displaced vertices. This improvement in reconstruction, at a time where theories predicting long-lived particles are ubiquitous and relatively unexplored, provides a golden opportunity to search for them using existing colliders, detectors, and dataset.

This thesis presents a new search for long-lived Heavy Neutral Leptons in events with di-lepton displaced vertices taking advantage of the aforementioned improvements in the ATLAS reconstruction algorithm applied to data collected between 2015 and 2018.~\Cref{chap:theory} outlines the fundamental structure of the Standard Model and lists the open problems that plague it. An extension to the Standard Model in the form of long-lived sterile neutrinos is presented. This extension forms the baselines model used in the analysis described in this dissertation. The apparatus used to test this model is the ATLAS experiment at the Large Hadron Collider, both of which are described in~\cref{chap:experiment}, along with the techniques used to collect data and stitch the readout signals from the detector into individual physical objects such as particles and their decays. The overview of this analysis is presented in~\cref{chap:ana_overview} with the exact goals set out to be achieved. The various steps of the analysis method and the statistical structure of extracting the strength of the model are detailed in~\cref{chap:ana_strategy}, followed by the results in~\cref{chap:results}.~\Cref{chap:conclusion} summarizes the inferences of this search and lists out possible improvements in the future versions of this adventure. My contributions to the analysis and to other projects in ATLAS are summarized in~\cref{chap:pers_contri} of the appendix.